Social Participation Ontology: community documentation, enhancements and use examples

### 2015-01-09 paper.tex
atualizando com mudancas poucas na secao da ops p continuar em breve

Followng the exposition in Section~\ref{sec:into}, from the CVSP the OSP was conceived. This section makes four considerations about OSP: first is label standardization and an exhibition of implemented and unimplemented CVSP classes, properties and restrictions. Features present in Figure~\ref{fig:v1}, but not present in the community release, are fully implemented in Section~\ref{impl}. Elementary further specification of subclasses is addressed in Section~\ref{downwards}. Examples of usage are addressed in Section~\ref{examplesUsage}.

>>>>

This section makes four considerations about the \ops: first is label standardization and an exhibition of implemented and unimplemented \vcps\ classes, properties and restrictions. Features present in Figure~\ref{fig:v1}, but not present in the community release, are fully described in Section~\ref{impl}. Elementary further specification of subclasses is addressed in Section~\ref{downwards}. Examples of usage are addressed in Section~\ref{examplesUsage}.
